Interpolation and Extrapolation Performance Measurement of Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium Carbon Steel

### 2023-10-16 Metals-2023.tex
Rename final production article

%=================================================================
% MDPI internal commands - do not modify
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{13}
\issuenum{1}
\articlenumber{633}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{Academic Editor: Ji Hoon Kim %MDPI: Please add it.
}
\datereceived{ 10 February 2023}
\daterevised{ 16 March 2023} % Comment out if no revised date
\dateaccepted{20 March 2023}
\datepublished{22 March 2023 }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/10.3390/met13030633} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-5360-5121}

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha $^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)\\
$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St. W., Montréal, QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}

@@

% Keywords
\keyword{artificial neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}

@@

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\midrule
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely $1050~\celsius$, $1100~\celsius$, $1150~\celsius$, $1200~\celsius$, and $1250~\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$, and $5~\ps$.
\begin{figure}[H]

@@

Figure \ref{fig:Micrography}a shows the microstructure obtained when the sample is held at $1260~\celsius$ for $5$ minutes and rapidly cooled to room temperature. From this image, large grains can be observed.
On the other hand, Figure \ref{fig:Micrography}b shows the microstructure after compression at $1150~\celsius$ with a $0.001~\ps$ strain rate.
To obtain this, the sample is heated up to $1260~\celsius$, then held for $5$ minutes and cooled down to $1150~\celsius$ to be held at this temperature for $1$ minute before compression.
After compression, the sample is rapidly cooled to room temperature to preserve the microstructure.
From this image, full recrystallization can be observed and is in correlation with Figure \ref{fig:RawData}, where after the peak, a steady stress is observed that describes the end of the recrystallization.

@@

\includegraphics[width=0.99\columnwidth]{Figures/CompExp-JC-6}
\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson--Cook model.}
\label{fig:CompExp-JC-6}
\end{figure}
The JC model is unable to describe the evolution of the average flow stress for all strain and strain rate levels. The experimental flow stresses show a growth and then a decrease with strain, especially for low strain rates, while the JC model, by its formulation, only allows an increasing evolution of the flow stress $\sigma^y$ as a function of the strain independently of the strain rate value.
The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
As expected, the mathematical formulation of the Johnson--Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
Since most of the parameters are identified at low strain rates ($A$, $B$, and $n$), this results in a very poor fit of the model to the experimental data.

The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the mean absolute relative error ($\MARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$, and $N$ is the total number of data points used to compute those coefficients (in our case $N$ = 21,000).
For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law especially in the case of a highly nonlinear functions because it only shows the correlation of the model with respect to the data and not its accuracy.
A good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction; we, therefore, avoided its use in our analysis.

@@

\begin{figure}[H]
\includegraphics[width=0.99\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Modified-Zerilli--Armstrong model.}
\label{fig:CompExp-MZA-6}
\end{figure}

%----------------------------------------------------------------------------------
\subsection{The Hansel--Spittel Model\label{sec:HSmodel}}
%----------------------------------------------------------------------------------

@@

In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.
From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} allowed computing the parameters reported in Table
 \ref{tab:HS}.

@@

A comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6}, where the dots represent the experimental values and the solid lines are the values predicted by the Hansel--Spittel flow law.
For the HS model, $\MARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
It appears that both this model and the previous ones do not adequately predict the experimental one, and the difference is relatively significant for all strain rates below $1~\ps$.
This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong nonlinear behavior observed for low strain rate values.
The DRX phenomenon cannot be reproduced by this type of model.

@@

Figure \ref{fig:CompExp-AR-6} shows a comparison of the values predicted by the Arrhenius model and the experimental values.
The difference between the experimental and predicted values is small.
However, for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is unable to predict the softening.
For the AR model, $\MARE=3.56~\%$ and $\RMSE=2.18~\MPa$.

@@

Figure \ref{fig:CompExp-PTM-6} presents a comparison of the values predicted by the PTM model and the experimental values.
The PTM model is suitable for describing the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$, the prediction is not very good.
The deviation between the predicted values and the experimental values for other strain rates is relatively low.
For the PTM model, $\MARE=4.79~\%$ and $\RMSE=4.59~\MPa$, which is an overall worse performance than the AR model.

@@

Neural networks generally have two uses: classification and regression.
The first is the ability to classify data into different groups, for example to distinguish between images of cats and dogs.
The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after training, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is achieved by the above-identified analytical models.
The main difference is that this approximation is not linked to a fixed mathematical formulation (as in the JC, MZA, AR, HS, and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
A feed-forward ANN, as used in our application, contains an input layer, an output layer, and a number of hidden layers ($2$ in our case).
Each layer of neurons is connected to the one before it and the one after it by weighted connections.
Thus, all the neurons of the $k^{th}$ layer are connected to all the neurons of the ($k-1^{th}$) layer, as shown in~Figure~\ref{fig:ANN-2HL}.
\begin{figure}[H]

\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
\label{fig:ANN-2HL}
\end{figure}

Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

The Python program used for training the neural network was developed using the specialized Python library, Tensorflow \cite{Abadi-2016}.
The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
The training data were those from the tests presented in Section \ref{sec:ComTestResults} and were composed of 21,000 quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
The training was performed on the basis of $5000$ epochs of the experimental dataset.
It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.
Figure \ref{fig:ANN-6-conv} shows the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$ during the training phase.
\begin{figure}[H]
\includegraphics[width=0.7\columnwidth]
{Figures/Conv-ANN-6}
\caption{Convergence of the ANN model during the training phase.}
\label{fig:ANN-6-conv}
\end{figure}
As can be seen in this figure, after $5000$ epochs, we can consider that we have reached a stationary state of the model training, such that it is useless to continue with the training~phase.

\textls[-25]{Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data, similarly to what was done with the analytical models.
One can either use the model directly by providing it with new input data or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in Appendix \ref{sec:Appendix}.}

@@

\caption{Accuracy coefficients for all the analyzed models.}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCC}
\toprule
\textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\
\midrule
$\MARE(\%)$ & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\
\bottomrule
\end{tabularx}
\label{tab:Errors}
\end{table}
From Table \ref{tab:Errors}, we can see that the ANN model has a much better predictive capacity than all the analytical models presented in the above sections.
Globally, the values of $\MARE$ and $\RMSE$ are six-times lower than with the best of the analytical models, \ie, the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.

The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at a low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and, more particularly, at low strain rates.
The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}--\ref{fig:CompExp-PTM-6} and \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.

@@

For interpolation validation, the chosen omitted strain rate was $\mdot\varepsilon=1~\ps$, and those used for identification (or training for the ANN) were the five others, \ie, $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
All models were re-identified from the same experimental data on a dataset corresponding to five strain rates and five temperatures.

@@

Table \ref{tab:IntVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the five identified strain rates (lines referred as id. $\mdot\varepsilon$), the six strain rates (lines referred as all $\mdot\varepsilon$), or only on the strain rate $\mdot\varepsilon=1~\ps$.
\begin{table}[H]
\centering{}
\caption{Accuracy coefficients of interpolation for all models with $\mdot\varepsilon=1~\ps$.}

>>>>

%=================================================================
% MDPI internal commands - do not modify
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{13}
\issuenum{3}
\articlenumber{633}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{Academic Editor: {Ji Hoon Kim} %MDPI: Please add it.
}
\datereceived{ 10 February 2023}
\daterevised{ 16 March 2023} % Comment out if no revised date
\dateaccepted{20 March 2023}
\datepublished{22 March 2023}
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/10.3390/\linebreak met13030633} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}
\newcommand{\hlok}[1]{\colorbox{green}{#1}}

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-5360-5121}
\newcommand{\orcidauthorD}{0000-0002-0815-1984}

% Authors, for the paper (add full first names)
\Author{{Pierre Tize Mha} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading. All names are correct
$^{1}$\orcidD{}, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; {ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)} %MDPI: We added emails from our system. Please confirm. OK
\\
$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St. W., \mbox{Montréal, QC H3C 1K3, Canada}; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); \mbox{mohammad.jahazi@etsmtl.ca (M.J.)}}

@@

% Keywords
\keyword{{artificial} %mdpi: please check the first letter format (uppercase/lowercase) for every word in keywords. please check all the keywords. we suggest to use lowercase if the uppercase is not necessary: OK
neural network; constitutive flow law; analytical flow law; interpolation; \linebreak extrapolation; Gleeble}

@@

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\midrule
{{Wt}%MDPI: Is the bold necessary?. You can remove the bold, if it does not correspond to the editorial line of the journal.
~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely $1050~\celsius$, $1100~\celsius$, $1150~\celsius$, $1200~\celsius$, and $1250~\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$, and $5~\ps$.

\vspace{2pt}
\begin{figure}[H]

@@

Figure \ref{fig:Micrography}a shows the microstructure obtained when the sample is held at $1260~\celsius$ for $5$~min and rapidly cooled to room temperature. From this image, large grains can be observed.
On the other hand, Figure \ref{fig:Micrography}b shows the microstructure after compression at $1150~\celsius$ with a $0.001~\ps$ strain rate.
To obtain this, the sample is heated up to $1260~\celsius$, then held for $5$ min and cooled down to $1150~\celsius$ to be held at this temperature for $1$ min before compression.
After compression, the sample is rapidly cooled to room temperature to preserve the microstructure.
From this image, full recrystallization can be observed and is in correlation with Figure \ref{fig:RawData}, where after the peak, a steady stress is observed that describes the end of the recrystallization.

@@

\includegraphics[width=0.99\columnwidth]{Figures/CompExp-JC-6}
\caption{{Comparison} %MDPI: Many figures are very similar. Please confirm there is no duplicate figure. No, every figure is different, the name of the figure correspond to the section, and everything is OK.
 between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson--Cook model.}
\label{fig:CompExp-JC-6}
\end{figure}
The JC model is unable to describe the evolution of the average flow stress for all strain and strain rate levels. The experimental flow stresses show a growth and then a decrease with strain, especially for low strain rates, while the JC model, by its formulation, only allows an increasing evolution of the flow stress $\sigma^y$ as a function of the strain independently of the strain rate value.
The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
As expected, the mathematical formulation of the Johnson--Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
Since most of the parameters are identified at low strain rates ($A$, $B$, and $n$), this results in a very poor fit of the model to the experimental data.

The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the mean absolute relative error ($\MARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$, and $N$ is the total number of data points used to compute those coefficients (in our case $N$ = 21,000).
For the JC model, $\MARE=14.05\%$ and $\RMSE=12.00~\MPa$.
As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law especially in the case of a highly nonlinear functions because it only shows the correlation of the model with respect to the data and not its accuracy.
A good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction; we, therefore, avoided its use in our analysis.

@@

\begin{figure}[H]
\includegraphics[width=0.93\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Modified-Zerilli--Armstrong model.}
\label{fig:CompExp-MZA-6}
\end{figure}

\vspace{-10pt}
%----------------------------------------------------------------------------------
\subsection{The Hansel--Spittel Model\label{sec:HSmodel}}
%----------------------------------------------------------------------------------

@@

In the present study, the best results were obtained by taking the model defined by only the first 7 $m_i$ terms of the Equation (\ref{eq:HS}), so that $m_8=0$.
From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} allowed computing the parameters reported in Table
 \ref{tab:HS}.

@@

A comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6}, where the dots represent the experimental values and the solid lines are the values predicted by the Hansel--Spittel flow law.
For the HS model, \mbox{$\MARE=7.75\%$} and $\RMSE=3.80~\MPa$.
It appears that both this model and the previous ones do not adequately predict the experimental one, and the difference is relatively significant for all strain rates below $1~\ps$.
This shows that this model is not appropriate for the characterization of this alloy, particularly because of the strong nonlinear behavior observed for low strain rate values.
The DRX phenomenon cannot be reproduced by this type of~model.

@@

Figure \ref{fig:CompExp-AR-6} shows a comparison of the values predicted by the Arrhenius model and the experimental values.
The difference between the experimental and predicted values is small.
However, for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is unable to predict the softening.
For the AR model, $\MARE=3.56\%$ and $\RMSE=2.18~\MPa$.

@@

Figure \ref{fig:CompExp-PTM-6} presents a comparison of the values predicted by the PTM model and the experimental values.
The PTM model is suitable for describing the flow behavior of medium carbon steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$, the prediction is not very good.
The deviation between the predicted values and the experimental values for other strain rates is relatively low.
For the PTM model, $\MARE=4.79\%$ and $\RMSE=4.59~\MPa$, which is an overall worse performance than the AR model.

@@

Neural networks generally have two uses: classification and regression.
The first is the ability to classify data into different groups, for example to distinguish between images of cats and dogs.
The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after training, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is achieved by the above-identified analytical models.
The main difference is that this approximation is not linked to a fixed mathematical formulation (as in the JC, MZA, AR, HS, and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
A feed-forward ANN, as used in our application, contains an input layer, an output layer, and a number of hidden layers ($2$ in our case).
Each layer of neurons is connected to the one before it and the one after it by weighted connections.
Thus, all the neurons of the $k^{th}$ layer are connected to all the neurons of the ($k-1^{th}$) layer, as shown in~Figure~\ref{fig:ANN-2HL}.

\vspace{-2pt}
\begin{figure}[H]

\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{{Two} %MDPI: Should green and red dot be explained?. Caption modified.
 hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
\label{fig:ANN-2HL}
\end{figure}

Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output {of the} %MDPI: We suggest to remove the superscript and italic format of ``th''. Please check all the ``th''. Notation has been changed following your request.
  $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

The Python program used for training the neural network was developed using the specialized Python library, Tensorflow \cite{Abadi-2016}.
The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
The training data were those from the tests presented in Section \ref{sec:ComTestResults} and were composed of 21,000 quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
The training was performed on the basis of $5000$ epochs of the experimental dataset.
It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16~GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.
Figure \ref{fig:ANN-6-conv} shows the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$ during the training phase.
\begin{figure}[H]
\includegraphics[width=0.7\columnwidth]
{Figures/Conv-ANN-6}
\caption{Convergence of the ANN model during the training phase.}
\label{fig:ANN-6-conv}
\end{figure}
As can be seen in this figure, after $5000$ epochs, we can consider that we have reached a stationary state of the model training, such that it is useless to continue with the training~phase.

\textls[-25]{Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data, similarly to what was done with the analytical models.
One can either use the model directly by providing it with new input data or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in {Appendix} %MDPI: We changed Appendix to Appendix A. OK
 \ref{sec:Appendix}.}

@@

\caption{Accuracy coefficients for all the analyzed models.}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCC}
\toprule
\textbf{Coefficients} & \textbf{JC} & \textbf{MZA} & \textbf{HS} & \textbf{AR} & \textbf{PTM} & \textbf{ANN} \\
\midrule
$\MARE(\%)$ & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\
\bottomrule
\end{tabularx}
\label{tab:Errors}
\end{table}
From Table \ref{tab:Errors}, we can see that the ANN model has a much better predictive capacity than all the analytical models presented in the above sections.
Globally, the values of $\MARE$ and $\RMSE$ are six-times lower than with the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of the hot forming of alloys \cite{Liang-2022}.

The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at a low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and, more particularly, at low strain rates.
The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}{--}%MDPI: We changed ``to'' to en dash. OOPS, there is a mistake, it's figures 6,7,8,9,10, and 13. Figures 11 and 12 cannot be included in this list. I updated the cross references.
\ref{fig:CompExp-PTM-6} and \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.

@@

For interpolation validation, the chosen omitted strain rate was $\mdot\varepsilon=1~\ps$, and \linebreak those used for identification (or training for the ANN) were the five others, \ie \linebreak \mbox{$\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$}.
All models were re-identified from the same experimental data on a dataset corresponding to five strain rates and five temperatures.

@@

Table \ref{tab:IntVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the five identified strain rates (lines referred as id. $\mdot\varepsilon$), the six strain rates (lines referred as all $\mdot\varepsilon$), or only on the strain rate $\mdot\varepsilon=1~\ps$.

\vspace{-2pt}
\begin{table}[H]
\centering{}
\caption{Accuracy coefficients of interpolation for all models with $\mdot\varepsilon=1~\ps$.}
